The Astropy Project:

### 2017-09-20 main.tex
Update on Overleaf.

@@

\subsection{Visualization}
wcsaxis, rgb, histograms comes to mind.Can use more publicity and also makes good images to include in the paper.

\subsection{Statistics}
%Crawford and JV

>>>>

\section{Notes and guidelines (to be removed)}

\begin{itemize}
	\item Right now, we don't foresee needing to include code in this paper. But, if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository. 
\end{itemize}

@@

\subsection{Visualization}
% Larry, Tom R.

wcsaxis, rgb, histograms comes to mind.Can use more publicity and also makes good images to include in the paper.

\subsection{Statistics}
% Steve C. and Jake V.
